### 2023-01-25 definitions.tex
Up

@@

\textcolor{blue}{
compute the sets of $(I,J,k)$ st S is resilient.\\
max des I,J possibles \\
remark: $k$-resilienc $\leq$ bounded Resilience $\leq$ Resilience.  AVERIFIER !!!
}

@@

\begin{proposition}\label{reductions}
coverability, liveness, home state and reachability reduce to resilience.
\end{proposition}

@@

\begin{itemize}
\item $J=\uparrow s$ et $I=\uparrow x$ then this particular resilience is coverability of $x$ from $s$.
\item $J=\{s\}$ and $I=\{x\}$ this particular resilience is reachability of $x$ from $s$.
\item $J=S = \downarrow S$
\end{itemize}
Let $J=\downarrow S = S$ and $I = \uparrow t$ where $t \in S$. Now resilience remains to the following property: $\forall s' \in S,  \exists s'' \in I, ~ s' \rightarrow^{*} s''$. Let us apply this property to LCS with $I = \uparrow (q,\epsilon) = (q, \Sigma^*)$. This property, $\forall s' \in S,  \exists w \in \Sigma^* $ such that $ ~ s' \rightarrow^{*} (q,w)$ expresses that there is an infinite run passing infinitely often through the control-state $q$; this LTL-property has been proved undecidable for Lossy Channel Systems (LCS) \cite{DBLP:conf/icalp/AbdullaJ94}.
Since LCS are effective WSTS with strong monotony (with an adequate semantics), we conclude.

@@

\alain{cette dernière propriété fait penser à la $t$-liveness dans un rdPetri ou n'importe quel modèle monotone..qui peut s'exprimer par $ ~ \forall s' \in S ~ (s \rightarrow^* s') \implies \exists s'' \in U_t ~ s' \rightarrow^{*} s''$ ? avec $U_t=\uparrow \pred(t)$=la clôture par le haut des préconditions pour déclencher la transition $t$}
\end{proof}

@@

\begin{proof} \alain{à relire/refaire}
Since liveness is undecidable for reset PN that are WSTS with strong monotony, from Proposition \ref{reductions}, we deduce that resilience is undecidable for WSTS with strong monotony.
  \textcolor{red}{à faire Mathieu}
\end{proof}

>>>>

\begin{remark} 
We require $U$ to be upward-closed, as, in the general case if we lift restrictions on $U$ and $D$, then reachability reduces itself to resilience. Indeed, the particular resilience problem where we take $D = \{s\}$ and $U = \{x\}$ is reachability of $x$ from $s$, and thus generally undecidable for WSTS. 
\end{remark}

@@

\textcolor{blue}{
compute the sets of $(I,J,k)$ st S is resilient.\\
max des I,J possibles \\
}

\begin{remark} 
$k$-resilienc $\leq$ bounded Resilience $\leq$ Resilience.  \textcolor{red}{AVERIFIER !!}
\end{remark}

@@

\begin{proposition}\label{reductions}
coverability, liveness, home state 
%and reachability
 reduce to resilience.
\end{proposition}

@@

\begin{itemize}
\item $J=S= \downarrow S$ et $I=\uparrow x$ then this particular resilience is coverability of $x$ from $s$.
%\item $J=\{s\}$ and $I=\{x\}$ this particular resilience is reachability of $x$ from $s$.

\item $t$-liveness c'est la résilience avec $J=S$ et $I = \uparrow \pred(t)$.
\end{itemize}

\textcolor{red}{  Let $J=\downarrow S = S$ and $I = \uparrow t$ where $t \in S$. Now resilience remains to the following property: $\forall s' \in S,  \exists s'' \in I, ~ s' \rightarrow^{*} s''$. Let us apply this property to LCS with $I = \uparrow (q,\epsilon) = (q, \Sigma^*)$. This property, $\forall s' \in S,  \exists w \in \Sigma^* $ such that $ ~ s' \rightarrow^{*} (q,w)$ expresses that there is an infinite run passing infinitely often through the control-state $q$; this LTL-property has been proved undecidable for Lossy Channel Systems (LCS) \cite{DBLP:conf/icalp/AbdullaJ94}.
Since LCS are effective WSTS with strong monotony (with an adequate semantics), we conclude.}
\mathieu{À refaire}

@@

\alain{cette dernière propriété fait penser à la $t$-liveness dans un rdPetri ou n'importe quel modèle monotone..qui peut s'exprimer par $ ~ \forall s' \in S ~ (s \rightarrow^* s') \implies \exists s'' \in U_t ~ s' \rightarrow^{*} s''$ ? avec $U_t=\uparrow \pred(t)$=la clôture par le haut des préconditions pour déclencher la transition $t$}

@@

\begin{proof} \alain{à relire/refaire}
Since liveness is undecidable for reset PN that are WSTS with strong monotony, from Proposition \ref{reductions}, we deduce that resilience is undecidable for WSTS with strong monotony.
  \textcolor{red}{à faire Mathieu}

Let $J=\downarrow S = S$ and $I = \uparrow t$ where $t \in S$. Now resilience remains to the following property: $\forall s' \in S,  \exists s'' \in I, ~ s' \rightarrow^{*} s''$. Let us apply this property to LCS with $I = \uparrow (q,\epsilon) = (q, \Sigma^*)$. \textcolor{red}{This property, $\forall s' \in S,  \exists w \in \Sigma^* $ such that $ ~ s' \rightarrow^{*} (q,w)$ expresses that there is an infinite run passing infinitely often through the control-state $q$ (à prouver dans les deux sens!)}; this LTL-property has been proved undecidable for Lossy Channel Systems (LCS) \cite{DBLP:conf/icalp/AbdullaJ94}.
Since LCS are effective WSTS with strong monotony (with an adequate semantics), we conclude.

\mathieu{(Sketch)
$\forall s' \in S,  \exists w \in \Sigma^* $ such that $ ~ s' \rightarrow^{*} (q,w)$ 
expresses that there is an infinite
run passing infinitely often through the control-state $q$

d'abords direction 1

$\forall s' \in S,  \exists w \in \Sigma^* $ $ ~ s' \rightarrow^{*} (q,w)$      $\implies$   there is an infinite run passing infinitely often through ...

$(q,w) \to s \to^* (q,w')$

globalement

sinon

l'autre direction

si il y a un run infini

c'est là que ça bloquait si je me souviens bien quand on avait travaillé dessus au tableau.

Sinon il faut prouver que si on n'a pas le truc alors on n'a pas le run infini

Si on n'a pas le truc

On a $s'$ tel que si on arrive en $s'$ alors on ne peut plus retourner en $q$.

Et $s'$ est accessible

MAIS ça veut pas dire qu’il n’y a pas de run infini

Plutôt que le Recurrent State Problem (RSP) on peut se concentrer plutôt du coup sur la $t$-liveness telle que décrite plus haut

$t$-liveness s'exprime par $ ~ \forall s' \in S ~ (s \rightarrow^* s') \implies \exists s'' \in U_t ~ s' \rightarrow^{*} s''$ ? avec $U_t=\uparrow \pred(t)$=la clôture par le haut des préconditions pour déclencher la transition $t$

$t$-liveness c'est la résilience avec $J=S$ et $I = \uparrow \pred(t)$.

Vérifier que la $t$-liveness c'est indécidable pour les LCS.
}
